Modeling vertical-axis cross-flow turbine wakes

### 2015-03-12 paper.tex
Minor additions and removing template comments

\title{Modeling vertical-axis cross-flow turbine wakes} %Title of paper

@@

\begin{abstract}
% insert abstract here
\end{abstract}

@@

% Body of paper goes here. Use proper sectioning commands. 
% References should be done using the \cite, \ref, and \label commands
\section{}
%\label{}
\subsection{}
\subsubsection{}

% If in two-column mode, this environment will change to single-column format so that long equations can be displayed. 
% Use only when necessary.
%\begin{widetext}
%$$\mbox{put long equation here}$$
%\end{widetext}

% Figures should be put into the text as floats. 
% Use the graphics or graphicx packages (distributed with LaTeX2e).
% See the LaTeX Graphics Companion by Michel Goosens, Sebastian Rahtz, and Frank Mittelbach for examples. 
%
% Here is an example of the general form of a figure:
% Fill in the caption in the braces of the \caption{} command. 
% Put the label that you will use with \ref{} command in the braces of the \label{} command.
%
% \begin{figure}
% \includegraphics{}%
% \caption{\label{}}%
% \end{figure}

% Tables may be be put in the text as floats.
% Here is an example of the general form of a table:
% Fill in the caption in the braces of the \caption{} command. Put the label
% that you will use with \ref{} command in the braces of the \label{} command.
% Insert the column specifiers (l, r, c, d, etc.) in the empty braces of the
% \begin{tabular}{} command.
%
% \begin{table}
% \caption{\label{} }
% \begin{tabular}{}
% \end{tabular}
% \end{table}

@@

% Create the reference section using BibTeX:
\bibliography{your-bib-file}

\end{document}
%
% ****** End of file aiptemplate.tex ******

>>>>

\title{Modeling vertical-axis cross-flow turbine wakes}

@@

\begin{abstract}
The wake of a vertical-axis cross-flow turbine (CFT) is modeled numerically via
several techniques.
\end{abstract}

@@

\section{Introduction}

Araya et al. modeled the flow through a VAT array using leaky Rankine bodies
\cite{Araya2014}.

\section{Numerical models}

\section{Model verification}

\section{Model validation}

Models were validated against several open datasets.

@@

% Create the reference section using BibTeX:
\bibliography{library}

\end{document}
